Pyrovelocity Notebook Usage Example

### 2024-03-25 nbs/templates/user_example/user_example.qmd
feat(nbs): add user example to templates Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Pyrovelocity Notebook Usage Example
toc: true
number-sections: true
highlight-style: pygments
csl: bibstyle.csl
lightbox: auto
format:
  nature-pdf:
    natbibstyle: sn-nature
    # classoption:
    #   - lineno
    cite-method: citeproc
    keep-tex: true
  html:
    mainfont: Latin Modern Sans
    code-fold: false
    html-math-method: katex
    embed-resources: true
  docx: default
  ipynb: default
format-links: false
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
  keep-ipynb: true
  keep-md: true
author:
  - name: Pyrovelocity Team
    email: team@pyrovelocity.net
abstract: |
  This notebook demonstrates how to run Pyro-Velocity in a Jupyter notebook on
  downsampled data. The results are not expected to be meaningful, but the
  notebook demonstrates the usage workflow with both a short execution time and
  using limited resources. It attempts to support both Google Colab and local or
  remote Jupyter kernel servers. Links to a blank copy of the notebook are 
  provided below.
keywords: [single-cell transcriptomics, probabilistic modeling, dynamical systems, RNA velocity]
bibliography: references.bib
jupyter:
  jupytext:
    cell_metadata_filter: all
    cell_metadata_json: true
    notebook_metadata_filter: all
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: 1.0
      jupytext_version: 1.16.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
  language_info:
    name: python
  rise:
    scroll: true
    theme: black
  toc-autonumbering: true
  toc-showcode: false
  toc-showmarkdowntxt: false
---

<a target="_blank" href="https://colab.research.google.com/github/pinellolab/pyrovelocity/blob/530-nbwf/docs/source/notebooks/pyrovelocity_pypi_user_template.ipynb">
  <img 
    src="https://colab.research.google.com/assets/colab-badge.svg" 
    alt="Open In Colab"
    width="109" height="20"/>
</a> <a target="_blank" href="https://nbviewer.jupyter.org/github/pinellolab/pyrovelocity/blob/530-nbwf/docs/source/notebooks/pyrovelocity_pypi_user_template.ipynb">
  <img 
    src="https://raw.githubusercontent.com/jupyter/design/master/logos/Badges/nbviewer_badge.png"
    alt="Render with nbviewer" 
    width="109" height="20"/>
</a>

>>>>

---
title: Pyrovelocity Notebook Usage Example
toc: true
number-sections: true
highlight-style: pygments
csl: bibstyle.csl
lightbox: auto
format:
#   nature-pdf:
#     natbibstyle: sn-nature
#     # classoption:
#     #   - lineno
#     cite-method: citeproc
#     keep-tex: true
  html:
    html-math-method: katex
#     mainfont: Latin Modern Sans
#     code-fold: false
#     embed-resources: true
#   docx: default
#   ipynb: default
# format-links: [ipynb]
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
  # keep-ipynb: true
  # keep-md: true
author:
  - name: Pyrovelocity Team
    email: team@pyrovelocity.net
abstract: |
  This notebook demonstrates how to run Pyro-Velocity in a Jupyter notebook on
  downsampled data. The results are not expected to be meaningful, but the
  notebook demonstrates the usage workflow with both a short execution time and
  using limited resources. It attempts to support both Google Colab and local or
  remote Jupyter kernel servers. Links to a blank copy of the notebook are 
  provided below.
keywords: [single-cell transcriptomics, probabilistic modeling, dynamical systems, RNA velocity]
bibliography: references.bib
jupyter:
  jupytext:
    cell_metadata_filter: all
    cell_metadata_json: true
    notebook_metadata_filter: all
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: 1.0
      jupytext_version: 1.16.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
  language_info:
    name: python
  rise:
    scroll: true
    theme: black
  toc-autonumbering: true
  toc-showcode: false
  toc-showmarkdowntxt: false
---

<a target="_blank" href="https://colab.research.google.com/github/pinellolab/pyrovelocity/blob/530-nbwf/scripts/notebooks/user_example.ipynb">
  <img 
    src="https://colab.research.google.com/assets/colab-badge.svg" 
    alt="Open In Colab"
    width="109" height="20"/>
</a> <a target="_blank" href="https://nbviewer.jupyter.org/github/pinellolab/pyrovelocity/blob/530-nbwf/scripts/notebooks/user_example.ipynb">
  <img 
    src="https://raw.githubusercontent.com/jupyter/design/master/logos/Badges/nbviewer_badge.png"
    alt="Render with nbviewer" 
    width="109" height="20"/>
</a>
